### 2021-10-26 content/31.tooling-table.tex
more refs
More edits following review
references

		\textbf{ro-crate-excel} \citep{ro-crate-excel} & Data managers & JavaScript \\
		\multicolumn{4}{l}{\it Command-line tool to help create RO-Crates and HTML-readable rendering} \\

@@

		\textbf{ro-crate-py} \citep{ro-crate-py} & Developers & Python & Beta \\
		\multicolumn{4}{l}{\it Object-oriented Python library for reading/writing RO-Crate} \\

@@

        \textbf{SCHeMa} \citep{arxiv:2103.13138v1} & Workflow users & PHP & Alpha \\
        \multicolumn{4}{l}{\it Workflow execution using RO-Crate as exchange mechanism} \\

@@

		\textbf{RDA maDMP Mapper} \citep{doi:10.5281/zenodo.3922136} & Data Management Plan users & Python & Beta \\
		\multicolumn{4}{l}{\it Mapping between machine-actionable data management plans (maDMP) and RO-Crate\citep{doi:10.4126/frl01-006423291} } \\

@@

		\bottomrule
	\end{tabular}
	\caption{Applications and libraries implementing RO-Crate, targeting different types of users across multiple programming languages. Status is indicative as assessed by this work.}
	\label{tab:tools}
\end{table}

>>>>

		\textbf{ro-crate-excel} \citep{ro-crate-excel} & Data managers & JavaScript \\
		\multicolumn{4}{l}{\it Command-line tool to create/edit RO-Crates with spreadsheets} \\

@@

		\textbf{ro-crate-py} \citep{ro-crate-py} & Developers & Python & Beta \\
		\multicolumn{4}{l}{\it Object-oriented Python library for reading/writing RO-Crate and use by Jupyter Notebook} \\

@@

        \textbf{SCHeMa} \citep{vergoulis2021schema} & Workflow users & PHP & Alpha \\
        \multicolumn{4}{l}{\it Workflow execution using RO-Crate as exchange mechanism} \\

@@

		\textbf{RDA maDMP Mapper} \citep{doi:10.5281/zenodo.3922136} & Data Management Plan users & Python & Beta \\
		\multicolumn{4}{l}{\it Mapping between machine-actionable data management plans (maDMP) and RO-Crate \citep{doi:10.4126/frl01-006423291} } \\

@@

        \textbf{RO-Crates-and-Excel} \citep{doi:10.5281/zenodo.5068950} & Data Managers & Java (CLI) & Alpha \\
        \multicolumn{4}{l}{\it Describe column/data details of spreadsheets as RO-Crate using DataCube vocabulary} \\

		\bottomrule
	\end{tabular}
	\caption{Applications and libraries implementing RO-Crate, targeting different types of users across multiple programming languages. Status is indicative as assessed by this work (Alpha < Beta < Release Candidate (RC) < Release).}
	\label{tab:tools}
\end{table}
